Objects of class `ranktable`

### 2025-02-28 inst/curling.Rmd

for(i in seq_len(ncol(curling_table))){
    x <- curling_table[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + ordervec2supp(x[!is.na(x)])
}
summary(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```

>>>>

for(i in seq_len(ncol(curling_table))){
    x <- curling_table[,i]
    names(x) <- rownames(curling_table)
    curling2 <- curling2 + suppfun(x[!is.na(x)])
}
summary(curling2)
(curling2_maxp <- maxp(curling2))
pie(curling2_maxp)
```

### 2025-02-28 inst/eurodance.Rmd
consistentify "time to process" information

To cite the `hyper2` package in publications, please use @hankin2017_rmd;
takes about 20 minutes to process without cache.  The file
`eurodance2008.txt`, used below, is copied from "Eurovision Dance
Contest 2008", Wikipedia, accessed March 31, 2021.  First we specify
the matrix as appearing in the Wikipedia page:

@@

```{r,label=eachcolisorder,cache=TRUE}
eurodance <- hyper2()
for(i in seq_len(ncol(pref))){
	x <- pref[,i]
	eurodance %<>% `+`(ordervec2supp(x[!is.na(x)]))
}  # i loop closes
eurodance_maxp <- maxp(eurodance)
eurodance_maxp
pie(eurodance_maxp)
```

@@

```{r,label=simfish,cache=TRUE}
n <- 4000
LL <- rep(0,n)
for(i in seq_len(n)){
	jjstar <- sample(jury)
	names(jjstar) <- names(jury)
	LL[i] <- loglik(indep(eurodance_maxp),ordervec2supp(jjstar),log=FALSE)
}
```

```{r,label=comparelogliks}
plot(sort(LL),log="y")
p <- loglik(indep(eurodance_maxp),ordervec2supp(jury),log=FALSE)
abline(h=p)
```

>>>>

<font size="1"> (takes about twenty minutes to run without cache)
</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  The file `eurodance2008.txt`, used below, is copied
from "Eurovision Dance Contest 2008", Wikipedia, accessed March 31,
2021.  First we specify the matrix as appearing in the Wikipedia page:

@@

```{r,label=eachcolisorder,cache=TRUE}
eurodance <- hyper2()
for(i in seq_len(ncol(pref))){
	x <- pref[,i]
	eurodance %<>% `+`(suppfun(x[!is.na(x)]))
}  # i loop closes
eurodance_maxp <- maxp(eurodance)
eurodance_maxp
pie(eurodance_maxp)
```

@@

```{r,label=simfish,cache=TRUE}
n <- 4000
LL <- rep(0,n)
for(i in seq_len(n)){
	jjstar <- sample(jury)
	names(jjstar) <- names(jury)
	LL[i] <- loglik(indep(eurodance_maxp),suppfun(jjstar),log=FALSE)
}
```

```{r,label=comparelogliks}
plot(sort(LL),log="y")
p <- loglik(indep(eurodance_maxp),suppfun(jury),log=FALSE)
abline(h=p)
```

### 2025-02-28 inst/formula1.Rmd
consistentify "time to process" information

---
title: "formula1"
output: html_document
---

@@

**This Rmd file takes about two hours to run without cache.**

Formula 1 racing is an important and prestigious motor sport.  Here I
analyse a series of racing results using the `hyper2` package which
implements the Plackett-Luce likelihood function.

@@

L2017 <- hyper2(pnames=alldrivers) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
        suppressWarnings(o <- as.numeric(levels(o))[o])
        o[is.na(o)] <- 0
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	L2017 <- L2017 + ordervec2supp(o)
}  # for(i) loop closes
head(L2017)
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
mHP <- mHP[mHP > 1e-2]
mHP
pie(mHP)
```

>>>>

---
title: "formula1"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy from vignettes/
---

@@

<font size="1"> (takes about two hours to run without cache)
</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Formula 1 racing is an important and prestigious
motor sport.  Here I analyse a series of racing results using the
`hyper2` package which implements the Plackett-Luce likelihood
function.

@@

L2017 <- hyper2(pnames=alldrivers) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
        suppressWarnings(o <- as.numeric(levels(o))[o])
        o[is.na(o)] <- 0
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	L2017 <- L2017 + suppfun(o)
}  # for(i) loop closes
head(L2017)
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	cond <- details$conditions[i]
        jj <- suppfun(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	HP <- HP + pwa(suppfun(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
mHP <- mHP[mHP > 1e-2]
mHP
pie(mHP)
```

### 2025-02-28 inst/formula1_points.Rmd

```{r,calcH,cache=TRUE}
H <- hyper2(pnames=rownames(o))
 for(i in seq_len(ncol(o))){
	H <- H + ordervec2supp(o[,i])
}
head(H)
mL2017 <- maxp(H)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
pie(mL2017)
```

>>>>

```{r,calcH,cache=TRUE}
H <- hyper2(pnames=rownames(o))
 for(i in seq_len(ncol(o))){
	H <- H + suppfun(o[,i])
}
head(H)
mL2017 <- maxp(H)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
pie(mL2017)
```

### 2025-02-28 inst/ordertable_to_ranktable.Rmd

---
title: "The print method for class ranktable"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
Rank tables can be confusing.  The package includes a range of
functionality for dealing with them, including a bespoke print method.
Here, I discuss two cases: firstly, a tiny toy example, and secondly
the volvo ocean racing dataset.

# Toy dataset

```{r makeatoy}
OT <- cbind(1:5,c(1,5,2:4))
rownames(OT) <- letters[seq_len(nrow(OT))]
colnames(OT) <- c("J1","J2")
OT
```

@@

Note that it is possible to view object `RT` directly by removing
class `ranktable`:

```{r viewdirect}
class(RT)
class(RT) <- "matrix"  # removes "ranktable" from class list
RT
```

Note carefully that the second row of `RT` (which corresponds to the
second judge) does *not* match the second column of `OT`.  The way to
read the second row of `RT` is as follows.  We see the entries `1 3 4
5 2` indicating that the first choice was competitor 1 [viz `a`], the
second choice was competitor 3 [viz `c`], the third choice was
competitor 4 [viz `d`], fourth choice was competitor 5 [`e`] and fifth
choice was competitor 2 [`b`].  So the rows are *ranks* (see the
discussion in `rrank.Rd`).  But it is very tempting to read the second
row of `RT` as "judge 2 placed competitor `b` in third place", which
is wrong because this is interpreting the row as an *order*.  This is
why the print method is there.

# Volvo ocean racing dataset

@@

The above shows that the extraction method for `ranktable` objects is
not yet written; maybe one day I will get round to implementing
`[.ranktable()` (right now I am not 100% sure that this is a good
idea).  Note that simply restoring the `ranktable` class can be
misleading:

```{r nowmakerank3}
xx <- x[,1:3]
xx
class(xx) <- "ranktable"
xx
```

In the above, `NA`s are introduced because a `ranktable` object uses
the column names to store names of the competitors, and of course
extracting the first three columns means keeping only the first three
column names.  Observe that extraction after passing to
`ranktable_to_printable_object()` works nicely:

```{r showprintableobject}
ranktable_to_printable_object(x)[,1:3]
```

>>>>

---
title: "Objects of class `ranktable`"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Rank tables can be confusing.  The package includes
a range of functionality for dealing with them.  Here, I discuss two
cases: firstly, a tiny toy example, and secondly the volvo ocean
racing dataset.

### Toy dataset {-}

```{r makeatoy}
OT <- cbind(1:5,c(1,5,2:4))
rownames(OT) <- letters[seq_len(nrow(OT))]
colnames(OT) <- c("J1","J2")
OT <- ordertable(OT)
OT
```

@@

### Volvo ocean racing dataset {-}

@@

The above shows that the extraction method for `ranktable` objects is
not yet written; maybe one day I will get round to implementing
`[.ranktable()` (right now I am not 100% sure that this is a good
idea).
